\newpage
\phantomsection
%\chapter*{Declarations}
%\Large
\section*{Authorship Declaration}
%\normalsize
%\newline
I, \textit{insert your full name}, confirm that this dissertation and the work presented in it and my own achievement.
\begin{enumerate}
    \item Where I have consulted the published work of others this is always clearly attributed;
    \item Where I have quoted from the work of others the source is always given. With the exception of such quotations this dissertation is entirely my own work;
    \item I have acknowledged all main sources of help;
    \item If my research follows on from previous work or is part of any larger collaborative research project I have made clear exactly what was done by others and what I have contributed myself;
    \item I have read and understood the penalties associated with Academic Misconduct.
    \item I also confirm that I have obtained \textbf{informed consent} from all people I have involved in the work in this dissertation following the School's ethical guidelines.\\
\end{enumerate}


\large

\textbf{Type name:}	\textit{Your full name} 

\textbf{Date:} 1st May 2020\\

\textbf{Matriculation No:} XXXXXXXXX
\normalsize
\newpage
%\large
\section*{General Data Protection Regulation Declaration}
%\normalsize\\
Under the General Data Protection Regulation (GDPR) (EU) 2016/679, the University cannot disclose your grade to an unauthorised person. However, other students benefit from studying dissertations that have their grades attached.
\newline\\
\\
\textbf{Please sign your name under \textit{one} of the options below to state your preference.}
\newline\\
\\
The University may make this dissertation, with indicative grade, available to others.
\\
\newline
\\
\newline
\\
The University may make this dissertation available to others, but the grade may not be disclosed.
\\
\newline
\\
\newline
\\
\newline
The University may not make this dissertation available to others.



